On Thue Numbers

### 2020-01-30 draft.tex
Missing graphics, but complete

\bibliography{library.bib}
\begin{document}
\renewcommand{\figurename}{Fig.}
\includepdf[pages=-]{deckblatt.pdf}
\thispagestyle{empty}
\newpage
\tableofcontents
\thispagestyle{empty}
\newpage

@@

\begin{minipage}[c]{0.8\linewidth}
	\includegraphics[scale=0.3]{pics/ex_marx.png}

@@

	\includestandalone{pics/ex_3}
	\caption{$G$ constructed from $f$ \\edge gadgets are highlighted}

@@

	\includegraphics[scale=0.3]{/home/ted/git/reveal.js/Bilder_ba/1_7snout.png}
	\caption{The subgraph replacing an edge colored $y_j$ in the snout of $G$}

@@

\includegraphics[scale=0.5]{/home/ted/git/reveal.js/Bilder_ba/cgadget.png} 
\caption{A C-gadget \citep{Manin2008}}

@@

\includegraphics[scale=0.5]{/home/ted/git/reveal.js/Bilder_ba/ngadget.png} 
\caption{An N-gadget \citep{Manin2008}}

@@

\begin{figure}
\includestandalone{pics/pgadget}
\caption{Key vertices of the $P$-gadget and their connections}

>>>>

\bibliography{library.bib}
\begin{document}
\renewcommand{\figurename}{Fig.}
%\includepdf[pages=-]{deckblatt.pdf}
\thispagestyle{empty}
\newpage
\tableofcontents
\thispagestyle{empty}
\newpage

@@

%\begin{minipage}[c]{0.8\linewidth}
%	\includegraphics[scale=0.3]{pics/ex_marx.png}
%\end{minipage}

@@

%\begin{figure}[h]
%	\includestandalone{pics/ex_3}
%	\caption{$G$ constructed from $f$ \\edge gadgets are highlighted}
%\end{figure}

@@

%\begin{figure}[h]
%	\includegraphics[scale=0.3]{/home/ted/git/reveal.js/Bilder_ba/1_7snout.png}
%	\caption{The subgraph replacing an edge colored $y_j$ in the snout of $G$}
%\end{figure}

@@

%\begin{figure}[h]
%\includegraphics[scale=0.5]{/home/ted/git/reveal.js/Bilder_ba/cgadget.png} 
%\caption{A C-gadget \citep{Manin2008}}
%\end{figure}

@@

%\begin{figure}[h]
%\includegraphics[scale=0.5]{/home/ted/git/reveal.js/Bilder_ba/ngadget.png} 
%\caption{An N-gadget \citep{Manin2008}}
%\end{figure}

@@

%\begin{figure}
%\includestandalone{pics/pgadget}
%\caption{Key vertices of the $P$-gadget and their connections}
%\end{figure}
